---
title: "MatrixQCvis report"
output:   
    BiocStyle::html_document:
        toc_float: true
        mathjax: null
        self_contained: true
params:
    missingValue: TRUE
    se_r: NULL
    se_n: NULL
    se_t: NULL
    se_b: NULL
    se_i: NULL
    sample_hist: "name"
    sample_mosaic_f1: "name"
    sample_mosaic_f2: "name"
    mev_binwidth: 1
    mev_binwidthC: 1
    miv_binwidth: 1
    miv_binwidthC: 1
    mev_hist_category: NULL
    mev_upset_category: NULL
    miv_hist_category: NULL
    miv_upset_category: NULL
    int_log: TRUE
    int_violin: TRUE
    int_drift_data: "raw"
    int_drift_aggregation: "median"
    int_drift_category: "name"
    int_drift_orderCategory: NULL
    int_drift_level: NULL
    int_drift_method: "loess"
    int_ma_data: "raw"
    int_ma_group: NULL
    int_ma_plot: NULL
    int_hD_lines: FALSE
    int_ecdf_data: "raw"
    int_ecdf_sample: NULL
    int_ecdf_group: "all"
    int_dist_method: "euclidean"
    int_dist_label: "name"
    int_feat_selectFeat: NULL,
    int_feat_featLine: FALSE,
    dr_pca_center: TRUE
    dr_pca_scale: TRUE
    dr_pca_highlight: "none"
    dr_pca_x: "PC1"
    dr_pca_y: "PC1"
    dr_pcoa_method: "euclidean"
    dr_pcoa_highlight: "none" 
    dr_pcoa_x: "Axis.1"
    dr_pcoa_y: "Axis.2"
    dr_nmds_highlight: "none"
    dr_nmds_x: "MDS1"
    dr_nmds_y: "MDS2"
    dr_tsne_perplexity: 1
    dr_tsne_max_iter: 1000
    dr_tsne_initial_dims: 10
    dr_tsne_dims: 3
    dr_tsne_pca_center: TRUE
    dr_tsne_pca_scale: TRUE
    dr_tsne_highlight: "none"
    dr_tsne_x: "X1"
    dr_tsne_y: "X2"
    dr_umap_min_dist: 0.1
    dr_umap_n_neighbors: 15
    dr_umap_spread: 1
    dr_umap_highlight: "none"
    dr_umap_x: "X1"
    dr_umap_y: "X2"
    de_m_formula: NULL
    de_c_formula: NULL
    de_method: "ttest"
    de_fit_ttest: NULL
    de_fit_proDA: NULL
---


```{r style, echo = FALSE, results = 'asis'}
BiocStyle::markdown()
```

```{r env, include=FALSE, echo=FALSE, cache=FALSE}
library("knitr")
opts_chunk$set(stop_on_error = 1L)
suppressPackageStartupMessages(library("MatrixQCvis"))
```

```{r prepare_se, eval=TRUE, echo=FALSE}
se_r <- params$se_r
se_n <- params$se_n
se_t <- params$se_t
se_b <- params$se_b
se_i <- params$se_i
missingValue <- params$missingValue
```



This is an automatically-produced report from `shinyQC`. The analyzed data
contains `r nrow(se_r)` features and `r ncol(se_r)` samples. 

# Tab: Samples

## Histogram

Use the settings

- *Categorical variable = * `r params$sample_hist`.

```{r hist_sample, eval=TRUE, echo=FALSE}
tbl <- hist_sample_num(se = se_r, category = params$sample_hist)
hist_sample(tbl, category = params$category_hist)
```


## Mosaic
```{r mosaic_prepare, eval=TRUE, echo=FALSE}
if (!is.null(params$sample_mosaic_f1)) {
    called <- TRUE
    sample_mosaic_f1 <- params$sample_mosaic_f1
} else {
    called <- FALSE
    sample_mosaic_f1 <- colnames(SummarizedExperiment::colData(se_r))[1]
}
if (!is.null(params$sample_mosaic_f2)) {
    sample_mosaic_f2 <- params$sample_mosaic_f2
} else {
    sample_mosaic_f2 <- colnames(SummarizedExperiment::colData(se_r))[1]
}

```

`r if (!called) {"The mosaic plot was not called within the shiny application. Use default settings."}`

Use the settings 

- *Categorical variable 1 =* `r sample_mosaic_f1` and 
- *Categorical variable 2 =* `r sample_mosaic_f2`. 

```{r mosaic, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
mosaic(se = params$se_r, f1 = sample_mosaic_f1, f2 = sample_mosaic_f2)
```

```{r, eval=TRUE, echo=FALSE}
if (shiny::isRunning())
  shiny::setProgress(0.1)
```


`r if (missingValue) {"# Tab: Measured Values\n"}`

`r if (missingValue) {"## Barplot for samples\n"}`



```{r samples_memi_mev, eval=params$missingValue, echo=FALSE, message=FALSE, warning=FALSE}
tbl <- samples_memi(se_r)
barplot_samples_memi(tbl, measured = TRUE)  
```


`r if (missingValue) {"## Histogram Features\n"}`

```{r hist_feature_mev_prepare, eval=TRUE, echo=FALSE,message=FALSE, warning=FALSE}
if (!is.null(params$mev_binwidth)) {
    called <- TRUE
    binwidth <- params$mev_binwidth
} else {
    called <- FALSE
    binwidth <- 1
}
```


`r if (missingValue & !called) {"The 'Histogram Features' plot was not called within the shiny application. Use default settings."}`

`r if (missingValue) {"Use the settings"}`

`r if (missingValue) {"- *Binwidth =*"}`  `r if (missingValue) paste(binwidth, ".", sep = "")`
```{r hist_feature_mev, eval=params$missingValue, echo=FALSE, message=FALSE, warning=FALSE}
hist_feature(SummarizedExperiment::assay(se_r), measured = TRUE, 
    binwidth = binwidth)  
```

`r if (missingValue) {"## Histogram Features along variable\n"}`

```{r hist_feature_category_mev_prepare, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
if (!is.null(params$mev_binwidthC)) {
    called <- TRUE
    binwidth <- params$mev_binwidthC
    mev_hist_category <- params$mev_hist_category
} else {
    called <- FALSE
    binwidth <- 1
    mev_hist_category <- colnames(SummarizedExperiment::colData(se_r))[1]
}
```

`r if (missingValue & !called) {"The 'Histogram Features along variable' plot was not called within the shiny application. Use default settings."}`

`r if (missingValue) {"Use the settings"}`

`r if (missingValue) {paste("- *Variable for stratification =*", mev_hist_category, "and")}`
`r if (missingValue) {paste("- *Binwidth =* ", binwidth, ".", sep = "")}`


```{r hist_feature_category_mev, eval=params$missingValue, echo=FALSE, message=FALSE, warning=FALSE}
hist_feature_category(se_r, measured = TRUE, category = mev_hist_category,
    binwidth = binwidth)
```

`r if (missingValue) {"## Upset\n"}`

```{r upset_mev_prepare, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
if (!is.null(params$mev_upset_category)) {
    called <- TRUE
    mev_upset_category <- params$mev_upset_category
} else {
    called <- FALSE
    mev_upset_category <- colnames(SummarizedExperiment::colData(se_r))[1]
}

```

`r if (missingValue & !called) {"The 'Upset' plot was not called within the shiny application. Use default settings."}`

`r if (missingValue) {"Use the settings"}`

`r if (missingValue) {paste("- *Variable for stratification =* ", mev_upset_category, ".", sep = "")}`


```{r upset_mev, eval=params$missingValue, echo=FALSE}
upset_category(se_r, category = mev_upset_category, measured = TRUE)
```


```{r, eval=TRUE, echo=FALSE}
if (shiny::isRunning())
  shiny::setProgress(0.2)
```

`r if (missingValue) {"# Tab: Missing Values\n"}`

`r if (missingValue) {"## Barplot for samples\n"}`

```{r samples_memi_miv, eval=params$missingValue, echo=FALSE, message=FALSE, warning=FALSE}
tbl <- samples_memi(se_r)
barplot_samples_memi(tbl, measured = FALSE)
```

`r if (missingValue) {"## Histogram Features\n"}`

```{r hist_feature_miv_prepare, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
if (!is.null(params$miv_binwidth)) {
    called <- TRUE
    binwidth <- params$miv_binwidth
} else {
    called <- FALSE
    binwidth <- 1
}
```

`r if (missingValue & !called) {"The 'Histogram Features' plot was not called within the shiny application. Use default settings."}`

`r if (missingValue) {"Use the settings"}`

`r if (missingValue) {paste("- *Binwidth =* ", binwidth, ".", sep = "")}`
```{r hist_feature_miv, eval=params$missingValue, echo=FALSE, message=FALSE, warning=FALSE}
hist_feature(SummarizedExperiment::assay(se_r), measured = FALSE, 
    binwidth = binwidth)
```

`r if (missingValue) {"## Histogram Features along variable\n"}`

```{r hist_feature_category_miv_prepare, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
if (!is.null(params$miv_binwidthC)) {
    called <- TRUE
    binwidth <- params$miv_binwidthC
    miv_hist_category <- params$miv_hist_category
} else {
    called <- FALSE
    binwidth <- 1
    miv_hist_category <- colnames(SummarizedExperiment::colData(se_r))[1]
}
```

`r if (missingValue & !called) {"The 'Histogram Features along variable' plot was not called within the shiny application. Use default settings."}`

`r if (missingValue) {"Use the settings"}`

`r if (missingValue) {paste("- *Variable for stratification =*", miv_hist_category, "and")}`
`r if (missingValue) {paste("- *Binwidth =* ", binwidth, ".", sep = " ")}`

```{r hist_feature_category_miv, eval=params$missingValue, echo=FALSE, message=FALSE, warning=FALSE}
hist_feature_category(se_r, measured = FALSE, category = miv_hist_category,
    binwidth = binwidth)
```

`r if (missingValue) {"## Upset\n"}`

```{r upset_miv_prepare, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
if (!is.null(params$miv_upset_category)) {
    called <- TRUE
    miv_upset_category <- params$miv_upset_category
} else {
    called <- FALSE
    miv_upset_category <- colnames(SummarizedExperiment::colData(se_r))[1]
}
```

`r if (missingValue & !called) {"The 'Upset' plot was not called within the shiny application. Use default settings."}`

`r if (missingValue) {"Use the settings"}`

`r if (missingValue) {paste("- *Variable for stratification =* ", mev_upset_category, ".", sep = " ")}`

```{r upset_miv, eval=params$missingValue, echo=FALSE}
upset_category(se_r, category = miv_upset_category, measured = FALSE)
```

```{r, eval=TRUE, echo=FALSE}
if (shiny::isRunning())
  shiny::setProgress(0.25)
```

# Tab: Values

## Boxplot/Violin plot

```{r boxplot_prepare, eval=TRUE,echo=FALSE, message=FALSE, warning=FALSE}
if (!is.null(params$int_violin)) {
    called <- TRUE
    int_box_type <- int_violin <- params$int_violin
    int_log <- params$int_log
    int_violin <- if (int_violin == "violin") TRUE else FALSE
    int_log <- if (int_log == "log2") TRUE else FALSE
} else {
    called <- FALSE
    int_violin <- TRUE
    int_log <- FALSE
    int_box_type <- "violin"
}
```

`r if (!called) {"The 'Boxplot/Violin plot' was not called within the shiny application. Use default settings."}`

Use the settings 

- *Display log2 values? = * `r int_log` and 
- *Type of display = * `r int_box_type`.

```{r boxplot, eval=TRUE, echo=FALSE, warning=FALSE}
create_boxplot(SummarizedExperiment::assay(se_r), title = "raw",
    log2 = int_log, violin = int_violin)
create_boxplot(SummarizedExperiment::assay(se_n), title = "normalized",
    log2 = int_log, violin = int_violin)
create_boxplot(SummarizedExperiment::assay(se_t), title = "transformed",
    log2 = FALSE, violin = int_violin)
create_boxplot(SummarizedExperiment::assay(se_b), title = "batch corrected",
    log2 = FALSE, violin = int_violin)
create_boxplot(SummarizedExperiment::assay(se_i), title = "imputed",
    log2 = FALSE, violin = int_violin)
```

```{r, eval=TRUE, echo=FALSE}
if (shiny::isRunning())
  shiny::setProgress(0.32)
```

## Trend/drift
```{r drift_prepare, eval=TRUE,echo=FALSE, message=FALSE, warning=FALSE}
if (!is.null(params$int_drift_data)) {
    called <- TRUE
    int_drift_data <- params$int_drift_data
    int_drift_aggregation <- params$int_drift_aggregation
    int_drift_category <- params$int_drift_category
    int_drift_orderCategory <- params$int_drift_orderCategory
    int_drift_level <- params$int_drift_level
    int_drift_method <- params$int_drift_method
    
    if (int_drift_data == "raw") {
       se_tmp <- se_r
    }
    if (int_drift_data == "normalized") {
        se_tmp <- se_n
    }
    if (int_drift_data == "transformed") {
        se_tmp <- se_t
    }
    if (int_drift_data == "batch corrected") {
        se_tmp <- se_b
    }
    if (int_drift_data == "imputed") {
        se_tmp <- se_i
    }
    
} else {
    called <- FALSE
    int_drift_data <- "raw"
    se_tmp <- se_r
    int_drift_aggregation <- "sum"
    int_drift_category <- colnames(SummarizedExperiment::colData(se_r))[1]
    int_drift_orderCategory <- colnames(SummarizedExperiment::colData(se_r))[1]
    int_drift_level <- "all"
    int_drift_method <- "loess"
}
```

`r if (!called) {"The 'Trend/drift' plot was not called within the shiny application. Use default settings."}`

Use the settings 

- *Select variable = * `r int_drift_category`,  
- *Select level to highlight = * `r int_drift_level`, 
- *Select data input = * `r int_drift_data`, 
- *Select aggregation = * `r int_drift_aggregation`,
- *Select smoothing method = * `r int_drift_method`, and 
- *Select variable to order samples = * `r int_drift_orderCategory`.

```{r drift, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
driftPlot(se_tmp, aggregation = int_drift_aggregation,
    category = int_drift_category,
    orderCategory = int_drift_orderCategory,
    level = int_drift_level,
    method = params$int_drift_method)
```

## Coefficient of variation

```{r cv, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
a_r <- SummarizedExperiment::assay(se_r)
a_n <- SummarizedExperiment::assay(se_n)
a_t <- SummarizedExperiment::assay(se_t)
a_b <- SummarizedExperiment::assay(se_b)
a_i <- SummarizedExperiment::assay(se_i)

## calculate cv values
cv_r <- cv(a_r, "raw")
cv_n <- cv(a_n, "normalized")
cv_t <- cv(a_t, "transformed")
cv_b <- cv(a_b, "batch corrected")
cv_i <- cv(a_i, "imputed")

df <- data.frame(cv_r, cv_n, cv_t, cv_b, cv_i)
plotCV(df)
```


## Mean-sd plot

```{r meansdplot, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
vsn::meanSdPlot(a_t)
vsn::meanSdPlot(a_b)
vsn::meanSdPlot(a_i)
```

```{r, eval=TRUE, echo=FALSE}
if (shiny::isRunning())
  shiny::setProgress(0.4)
```

## MA plot
```{r maplot_prepare, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
if (!is.null(params$int_ma_group)) {
    called <- TRUE
    int_ma_group <- params$int_ma_group
    int_ma_data <- params$int_ma_data
    int_ma_plot <- params$int_ma_plot
    int_hD_lines <- params$int_hD_lines
} else {
    called <- FALSE
    int_ma_group <- "all"
    int_ma_data <- "raw"
    int_ma_plot <- "all"
    int_hD_lines <- FALSE
}
```

`r if (!called) {"The 'MA plot' was not called within the shiny application. Use default settings."}`

Use the settings 

- *group = * `r int_ma_group`,  
- *plot = * `r int_ma_plot`, 
- *Data set for the MA plot = * `r int_ma_data`, and
- *lines = * `r int_hD_lines`.

```{r maplot, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
tbl_r <- MAvalues(se_r, log2 = TRUE, group = int_ma_group)
tbl_n <- MAvalues(se_n, log2 = TRUE, group = int_ma_group)
tbl_t <- MAvalues(se_t, log2 = FALSE, group = int_ma_group)

if (shiny::isRunning())
  shiny::setProgress(0.5)


tbl_b <- MAvalues(se_b, log2 = FALSE, group = int_ma_group)
tbl_i <- MAvalues(se_i, log2 = FALSE, group = int_ma_group)
 
if (int_ma_data == "raw") {
    tbl <- tbl_r
}
if (int_ma_data == "normalized") {
    tbl <- tbl_n
}
if (int_ma_data == "transformed") {
    tbl <- tbl_t
}
if (int_ma_data == "batch corrected") {
    tbl <- tbl_b
}
if (int_ma_data == "imputed") {
    tbl <- tbl_i
}
 
MAplot(tbl, group = int_ma_group,
    plot = int_ma_plot)

d_r <- hoeffDValues(tbl_r, name = "raw")
d_n <- hoeffDValues(tbl_n, name = "normalized")
d_t <- hoeffDValues(tbl_t, name = "transformed")
d_b <- hoeffDValues(tbl_b, name = "batch corrected")

if (missingValue) {
    d_i <- hoeffDValues(tbl_i, name = "imputed")
    df <- data.frame(d_r, d_n, d_t, d_b, d_i)  
} else {
    df <- data.frame(d_r, d_n, d_t, d_b)
}

hoeffDPlot(df, lines = int_hD_lines)
```

```{r, eval=TRUE, echo=FALSE}
if (shiny::isRunning())
  shiny::setProgress(0.55)
```

## ECDF
```{r ecdf_prepare, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
if (!is.null(params$int_ecdf_sample)) {
    called <- TRUE
    int_ecdf_data <- params$int_ecdf_data
    int_ecdf_sample <- params$int_ecdf_sample
    int_ecdf_group <- params$int_ecdf_group
    
    if (int_ecdf_data == "raw") {
        se_tmp <- se_r
    }
    if (int_ecdf_data == "normalized") {
        se_tmp <- se_n
    }
    if (int_ecdf_data == "transformed") {
        se_tmp <- se_t
    }
    if (int_ecdf_data == "batch corrected") {
        se_tmp <- se_b
    }
    if (int_ecdf_data == "imputed") {
        se_tmp <- se_i
    }

} else {
    called <- FALSE
    int_ecdf_data <- "raw"
    int_ecdf_sample <- colnames(se_r)[1]
    int_ecdf_group <- "all"
    se_tmp <- se_r
}
```

`r if (!called) {"The 'ECDF' plot was not called within the shiny application. Use default settings."}`

Use the settings

- *Data set for the ECDF plot = * `r int_ecdf_data`,  
- *Sample = * `r int_ecdf_sample`, and
- *group = * `r int_ecdf_group`.

```{r ecdf, eval=TRUE, echo=FALSE, warning=FALSE}
ECDF(se_tmp, sample = int_ecdf_sample,
    group = int_ecdf_group)
```


## Distance matrix
```{r distSample_prepare, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
if (!is.null(params$int_ecdf_label)) {
    called <- TRUE
    int_dist_label <- params$int_dist_label
    int_dist_method <- params$int_dist_method
} else {
    called <- FALSE
    int_dist_label <- colnames(SummarizedExperiment::colData(se_r))[1]
    int_dist_method <- "euclidean"
}
```

`r if (!called) {"The 'Distance matrix' plots were not called within the shiny application. Use default settings."}`

Use the settings

- *annotation = * `r int_dist_label` and 
- *distance method = * `r int_dist_method`.

```{r distSample, eval=TRUE, echo=FALSE}
dist_mat_r <- distShiny(a_r, method = int_dist_method)
dist_mat_n <- distShiny(a_n, method = int_dist_method)
dist_mat_t <- distShiny(a_t, method = int_dist_method)
dist_mat_b <- distShiny(a_b, method = int_dist_method)

## plotting
distSample(d = dist_mat_r, se = se_r,
    label = int_dist_label, title = "raw")
sumDistSample(dist_mat_r, title = "raw")

distSample(d = dist_mat_n, se = se_n,
    label = int_dist_label, title = "normalized")
sumDistSample(dist_mat_n, title = "normalized")

distSample(d = dist_mat_t, se = se_t,
    label = int_dist_label, title = "transformed")
sumDistSample(dist_mat_t, title = "transformed")

distSample(d = dist_mat_b, se = se_b,
    label = int_dist_label, title = "batch corrected")
sumDistSample(dist_mat_b, title = "batch corrected")

if (missingValue) {
    dist_mat_i <- distShiny(a_i, method = int_dist_method)
    distSample(d = dist_mat_i, se = se_i,
        label = int_dist_label, title = "imputed")
    sumDistSample(dist_mat_i, title = "imputed")  
}

```

## Features

```{r features_prepare, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
if (!is.null(params$int_feat_selectFeat)) {
    called <- TRUE
    int_feat_selectFeat <- params$int_feat_selectFeat
    int_feat_featLine <- params$int_feat_featLine
} else {
    called <- FALSE
    int_feat_selectFeat <- rownames(se_r)[1]
    int_feat_featLine <- FALSE
}
```

`r if (!called) {"The 'Features' plots were not called within the shiny application. Use default settings."}`

Use the settings

- *Select feature = * `r int_feat_selectFeat` and 
- *lines = * `r int_feat_featLine`.

```{r features, eval=TRUE, echo=FALSE}
if (missingValue) {
    l_assays <- list(raw = a_r, normalized = a_n, 
      transformed = a_t, batch.corrected = a_b, imputed = a_i)
} else {
    l_assays <- list(raw = a_r, normalized = a_n,
      transformed = a_t, batch.corrected = a_b)
}

df_feature <- createDfFeature(l_assays, feature = int_feat_selectFeat)

## plotting
featurePlot(df_feature)
cvFeaturePlot(l_assays, lines = int_feat_featLine)
```

```{r, eval=TRUE, echo=FALSE}
if (shiny::isRunning())
  shiny::setProgress(0.6)
```

# Tab: Dimension Reduction

## PCA
```{r PCA_prepare, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
if (!is.null(params$dr_pca_highlight)) {
    called <- TRUE
    dr_pca_center <- params$dr_pca_center
    dr_pca_scale <- params$dr_pca_scale
    dr_pca_highlight <- params$dr_pca_highlight
    dr_pca_x <- params$dr_pca_x
    dr_pca_y <- params$dr_pca_y
} else {
    called <- FALSE
    dr_pca_center <- TRUE
    dr_pca_scale <- TRUE
    dr_pca_highlight <- "none"
    dr_pca_x <- "PC1"
    dr_pca_y <- "PC2"
}
```

`r if (!called) {"The 'PCA' plot was not called within the shiny application. Use default settings."}`

Use the settings 

- *x-axis = * `r dr_pca_x`, 
- *y-axis = * `r dr_pca_y`, 
- *scale = * `r dr_pca_scale`,
- *center = * `r dr_pca_center`, and 
- *Highlight = * `r dr_pca_highlight`. 

```{r PCA, eval=TRUE, echo=FALSE}
tbl <- ordination(a_i, type = "PCA",
    params = list(center = dr_pca_center, scale = dr_pca_scale))
explainedVar <- explVar(x = a_i, center = dr_pca_center, scale = dr_pca_scale)
ordinationPlot(tbl = tbl, se = se_r, highlight = dr_pca_highlight,
    explainedVar = explainedVar, x_coord = dr_pca_x, y_coord = dr_pca_y)
```


## PCoA
```{r PCoA_prepare, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
if (!is.null(params$dr_pcoa_highlight)) {
    called <- TRUE
    dr_pcoa_method <- params$dr_pcoa_method
    dr_pcoa_highlight <- params$dr_pcoa_highlight
    dr_pcoa_x <- params$dr_pcoa_x
    dr_pcoa_y <- params$dr_pcoa_y
} else {
    called <- FALSE
    dr_pcoa_method <- "euclidean"
    dr_pcoa_highlight <- "none"
    dr_pcoa_x <- "Axis.1"
    dr_pcoa_y <- "Axis.2"
}
```

`r if (!called) {"The 'PCoA' plot was not called within the shiny application. Use default settings."}`

Use the settings 

- *x-axis = * `r dr_pcoa_x`, 
- *y-axis = * `r dr_pcoa_y`, 
- *Distance measure = * `r dr_pcoa_method`, and 
- *Highlight = * `r dr_pcoa_highlight`. 

```{r PCoA, eval=TRUE, echo=FALSE}
tbl <- ordination(a_i, type = "PCoA",
    params = list(method = dr_pcoa_method))
ordinationPlot(tbl = tbl, se = se_r, highlight = dr_pcoa_highlight,
    explainedVar = NULL, x_coord = dr_pcoa_x, y_coord = dr_pcoa_y)
```

```{r, eval=TRUE, echo=FALSE}
if (shiny::isRunning())
  shiny::setProgress(0.65)
```

## NMDS
```{r NMDS_prepare, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
if (!is.null(params$dr_nmds_highlight)) {
    called <- TRUE
    dr_nmds_method <- params$dr_pcoa_method
    dr_nmds_highlight <- params$dr_nmds_highlight
    dr_nmds_x <- params$dr_nmds_x
    dr_nmds_y <- params$dr_nmds_y
} else {
    called <- FALSE
    dr_nmds_method <- "euclidean"
    dr_nmds_highlight <- "none"
    dr_nmds_x <- "MDS1"
    dr_nmds_y <- "MDS2"
}
```

`r if (!called) {"The 'NMDS' plot was not called within the shiny application. Use default settings."}`

Use the settings

- *x-axis = * `r dr_nmds_x`, 
- *y-axis = * `r dr_nmds_y`, 
- *Distance measure = * `r dr_nmds_method`, and 
- *Highlight = * `r dr_nmds_highlight`. 

```{r NMDS, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
tbl <- ordination(a_i, type = "NMDS", params = list(method = dr_nmds_method))

```
```{r NMDS_plot, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
ordinationPlot(tbl = tbl, se = se_r, highlight = dr_nmds_highlight,
    explainedVar = NULL, x_coord = dr_nmds_x, y_coord = dr_nmds_y)
```

## tSNE
```{r tSNE_prepare, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
if (!is.null(params$dr_tsne_highlight)) {
    called <- TRUE
    dr_tsne_perplexity <- params$dr_tsne_perplexity
    dr_tsne_max_iter <- params$dr_tsne_max_iter
    dr_tsne_initial_dims <- params$dr_tsne_initial_dims
    dr_tsne_dims <- params$dr_tsne_dims
    dr_tsne_pca_center <- params$dr_tsne_pca_center
    dr_tsne_pca_scale <- params$dr_tsne_pca_scale
    dr_tsne_highlight <- params$dr_tsne_highlight
    dr_tsne_x <- params$dr_tsne_x
    dr_tsne_y <- params$dr_tsne_y
} else {
    called <- FALSE
    dr_tsne_perplexity <- 1
    dr_tsne_max_iter <- 1000
    dr_tsne_initial_dims <- 10
    dr_tsne_dims <- 3
    dr_tsne_pca_center <- TRUE
    dr_tsne_pca_scale <- TRUE
    dr_tsne_highlight <- "none"
    dr_tsne_x <- "X1"
    dr_tsne_y <- "X2"
}
```

```{r, eval=TRUE, echo=FALSE}
if (shiny::isRunning())
  shiny::setProgress(0.73)
```

`r if (!called) {"The 'tSNE' plot was not called within the shiny application. Use default settings."}`

Use the settings 

- *x-axis = * `r dr_tsne_x`, 
- *y-axis = * `r dr_tsne_y`, 
- *Perplexity = * `r dr_tsne_perplexity`, 
- *Number of iterations = * `r dr_tsne_max_iter`, 
- *Number of retained dimensions in intial PCA = * `r dr_tsne_initial_dims`,
- *Output dimensionality = * `r dr_tsne_dims`, `scale =` `r dr_tsne_pca_scale`,
- *center = * `r dr_tsne_pca_center`, and 
- *Highlight = * `r dr_tsne_highlight`.

```{r tSNE, eval=TRUE, echo=FALSE}
tbl <- ordination(a_i, type = "tSNE", 
    params = list(perplexity = dr_tsne_perplexity, 
    max_iter = dr_tsne_max_iter, initial_dims = dr_tsne_initial_dims,
    dims = dr_tsne_dims, pca_center = dr_tsne_pca_center,
    pca_scale = dr_tsne_pca_scale))
ordinationPlot(tbl = tbl, se = se_r, highlight = dr_tsne_highlight,
    explainedVar = NULL, x_coord = dr_tsne_x, y_coord = dr_tsne_y)
```


## UMAP
```{r UMAP_prepare, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
if (!is.null(params$dr_umap_highlight)) {
    called <- TRUE
    dr_umap_min_dist = params$dr_umap_min_dist
    dr_umap_n_neighbors = params$dr_umap_n_neighbors
    dr_umap_spread = params$dr_umap_spread
    dr_umap_highlight = params$dr_umap_highlight
    dr_umap_x = params$dr_umap_x
    dr_umap_y = params$dr_umap_y
} else {
    called <- FALSE
    dr_umap_min_dist = 0.1
    dr_umap_n_neighbors = 15
    dr_umap_spread = 1
    dr_umap_highlight = "none"
    dr_umap_x = "X1"
    dr_umap_y = "X2"
}
```

`r if (!called) {"The 'UMAP' plot was not called within the shiny application. Use default settings."}`

Use the settings 

- *x-axis = * `r dr_umap_x`, 
- *y-axis = * `r dr_umap_y`, 
- *Minimum distance =* `r dr_umap_min_dist`, 
- *Number of neighbors =* `r dr_umap_n_neighbors`, 
- *Spread = * `r dr_umap_spread`, and
- *Highlight = * `r dr_umap_highlight`. 

```{r UMAP, eval=TRUE, echo=FALSE}
tbl <- ordination(a_i, type = "UMAP", 
    params = list(min_dist = dr_umap_min_dist, n_neighbors = dr_umap_n_neighbors,
        spread = dr_umap_spread))
ordinationPlot(tbl = tbl, se = se_r, highlight = dr_umap_highlight,
    explainedVar = NULL, x_coord = dr_umap_x, y_coord = dr_umap_y)
```


```{r, eval=TRUE, echo=FALSE}
if (shiny::isRunning())
  shiny::setProgress(0.87)
```



```{r DE_prepare,echo=FALSE, eval=TRUE}
m_formula <- params$de_m_formula
valid_m <- if (!is.null(m_formula)) TRUE else FALSE

c_formula <- params$de_c_formula
valid_c <- if (!is.null(c_formula)) TRUE else FALSE
```

`r if (valid_m | (valid_m & valid_c)) {"# Tab: DE\n~\n"}`
`r if (valid_m) {"The differential expression analysis was called with the model matrix formula:"}`
`r if (valid_m) {c_formula}`

`r if (valid_m & valid_c) {"The differential expression analysis was called with the contrast expression:"}`
`r if (valid_m) {c_formula}`


```{r DE, echo=FALSE, eval=TRUE}
if (valid_m & valid_c) {
    mM <- stats::model.matrix(m_formula, data = colData(se_r))
    cM <- limma::makeContrasts(contrasts = c_formula, levels = mM)

    if (params$de_method == "limma") {
        tT <- limma::topTable(params$de_fit_ttest, number = Inf, 
            adjust.method = "fdr", p.value = 0.05)
        tT <- cbind(name = rownames(tT), tT)
        volcanoPlot(tT, type = "ttest")
    }
    if (params$de_method == "proDA") {
        tT <- proDA::test_diff(fit = params$de_fit_proDA, 
            contrast = params$de_c_formula,
            sort_by = "adj_pval")
        volcanoPlot(tT, type = "proDA")
    }
}
```

```{r, eval=TRUE, echo=FALSE}
if (shiny::isRunning())
  shiny::setProgress(0.98)
```